---
title: "Class project R Code"
author: "Tz-Ruei Liu"
date: "April 21, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Read the data from excel into a data frame
```{r}
library(readxl)
dat <- read_excel("Project_Data_set.xlsx", sheet=1, range = "A1:D17")
dat
```

##Check the two-way interaction effects A:B, A:C, and B:C
```{r}
par(mfrow=c(1,3))
with(dat, interaction.plot(A,B,Time))
with(dat, interaction.plot(A,C,Time))
with(dat, interaction.plot(B,C,Time))
```

##Check the three-way interaction effect A:B:C
```{r}
par(mfrow=c(1,2))
with(dat, interaction.plot(B[A=='1'],C[A=='-1'],Time[A=='1'], xlab='B', ylab='Time', trace.label='C', main='A is +1' ))
with(dat, interaction.plot(B[A=='-1'],C[A=='-1'],Time[A=='-1'], xlab='B', ylab='Time', trace.label='C', main='A is -1'))

```

##Check the boxplot and observe how difference in levels of main factors affect the boiling time of milk (response variable)
```{r}
library(ggplot2)
ggplot(dat, aes(x = A, y = Time, fill = B)) + 
  geom_boxplot() + 
  facet_grid(~C)

```

##Perform an ANOVA on all factors and their intereaction effects and check which effects are signficant based on their p-values
```{r}
summary(aov(Time~A*B*C, data=dat))
```

##Apply the linear regression model and perform parameter estimations
```{r}
summary(lm(Time~A*B*C, data=dat))
```


##Model Diagnostic (check whether the residuals are normally distributed)
```{r}
aov_dat<-aov(Time~A*B*C, data=dat)
resid_dat <- residuals(aov_dat)
par(mfrow=c(1,2))
qqnorm(resid_dat)
qqline(resid_dat)
plot(aov_dat, which=2)
```

##To check for homoskedasticity, we create residual plots for by plotting residuals vs all three main factors A, B, C. We observe that residuals are equally and evenly distributed on high and low levels for all three factors.
```{r}
par(mfrow=c(1,3))
plot(as.character(dat$A), resid_dat, xlab="A", ylab="Residuals")
plot(as.character(dat$B), resid_dat, xlab="B", ylab="Residuals")
plot(as.character(dat$C), resid_dat, xlab="C", ylab="Residuals")
#bartlett.test(resid_dat, dat$C)
```












